Stack Safety as Security Property

### 2020-05-29 main.tex
Fix typo in main
Nit
From meeting

\title{Stack Safety as Security Property}
%\title{The Meaning of/What is Stack Safety}
\iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF
    and...?)}}\fi
}

@@

Contributions:
\begin{itemize}
\item A formal property capturing the informal understanding of what ``stack safety'' is.
\item Evidence that this property really does capture the folk intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism.
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\item TODO: Logic? Reasoning Principles?
\end{itemize}

>>>>

\title{Stack Safety as Security Property}
%\title{The Meaning of/What is Stack Safety}
\iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF
    and...?)}}
\fi

@@

Contributions:
\begin{itemize}
\item A formal property capturing the informal understanding of what ``stack safety'' is.
\item Evidence that this property really does capture the folk intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\item TODO: Logic? Reasoning Principles?
\end{itemize}

### 2020-05-29 props.tex
From meeting

    A policy is a general model of an enforcement mechanism, consisting of
    a set of policy states, \(\pol \in \POLS\), a policy initializer
    \(\pinit : \MACHS \rightharpoonup \POLS\), and a policy step function \(\pol \stepstopol \pol' :
    \POLS \rightharpoonup \POLS\). The initializer and step function are both partial functions,
    the former to reflect static guarantees (some initial states may not be valid at all) and
    the latter to reflect dynamic fail-stop behavior. We then define machine-policy pairs and
    a step function on them:

@@

    \[\frac{\mach_1 \stepstoobs{\obs} \mach_2 \hspace{.5cm} \pol_1 \stepstopol \pol_2}
           {\mpstate{\mach_1}{\pol_1} \stepstoobs{\obs}_P \mpstate{\mach_2}{\pol_2}}\]

@@

    We project the machine states from either machine trace with \(\pi_m\) and the observations with \(\pi_o\).
    An observational prefix \(\obsT_1 \lesssim \obsT_2\) means that the trace \(\obsT_1\) of observations is
    a prefix of \(\obsT_2\) up to the deletion of \(\tau\) observations:

@@

    \[\frac{\isinf(\MPT) \hspace{.5cm} \mathit{Obs}(\MPT) \lesssim \mathit{Obs}(\machT)}
           {\MPT \sim_P \machT}\]

    \[\frac{\neg \isinf(\MPT) \hspace{.5cm} \mathit{Obs}(\MPT) \simeq \mathit{Obs}(\machT)}
           {\MPT \sim_P \machT}\]

@@

  \paragraph{Call Maps and Returns}

    A {\it call map} identifies machine states that represent a call, abstracting away the explicit
    calling convention. Formally it maps some machine states to a number of arguments:
    \[\callmap \in \CALLMAPS = \mach \rightharpoonup \mathbb{N}\]

@@

    \[\begin{split}
      \ret{\mach_c}\ \mach_r \triangleq & \mach_r(\PCname) = \mach_c(\PCname)+1 \land \\
                                        & \mach_r(\SP) = \mach_c(\SP)
    \end{split}\]

@@

@@

      Observable confidentiality is concerned with whether high confidentiality data influences
      observable both behavior during and after a call. We define variants given the generalized notion
      of contours:
      \[\mach \approx_\contour \mach' \triangleq \forall \component .
        \contour(\component) = \LOWSEC \rightarrow \mach(\component) = \mach'(\component)\]

      Data that is high confidentiality within a callee due either to being in its caller's frame
      will become low confidentiality if the callee returns. We face a subtle distinction: 
      a callee treats the contents of its caller's frame as secrets, and they should not influence
      its behavior. Nor should the callee be able to influence behavior after its return based
      on the caller's secrets, for instance by copying them to registers that will later be output.
      But the caller itself may still adjust its behavior based on its own secrets. So our property
      relies on another rollback function to preserve changes made by the caller but remove other
      differences between variant states.

      In this case, a confidentiality rollback takes a contour and four states: two call states
      that will be variants, and two return states. It is not symmetric, regarding \(\mach_c\) and \(\mach_r\)
      as the ``real'' call and return, \(\mach_c'\) as a variant and \(\mach_r'\) as a return that follows it.
      \[\begin{split}
        & \mathit{roll}_C(\contour,\mach_c,\mach_c',\mach_r,\mach_r')(\component) = \\
        & \begin{cases}
          \mach_c(\component) & \text{if } C(\component) = \HIGHSEC \text{ and } \\
                  & \mach_c(\component) = \mach_r(\component) \text{ and }
                    \mach_c'(\component) = \mach_r'(\component) \\
          \mach_r'(\component) & \text{else} \\
        \end{cases}
      \end{split}\]

@@

>>>>

    \paragraph*{Policy}

    A policy is a general model of an enforcement mechanism,
    consisting of a set of policy states, \(\pol \in \POLS\) and a
    policy step function \((\mach, \pol) \stepstopol \pol' : \MACHS
    \times \POLS \rightharpoonup \POLS\).

    The initializer and step function are both partial functions,
    the former to reflect static guarantees (some initial states may not be valid at all) and
    the latter to reflect dynamic fail-stop behavior. We then define machine-policy pairs and
    a step function on them:

@@

    \[\frac{\mach_1 \stepstoobs{\obs} \mach_2 \hspace{.5cm} (\mach_1, \pol_1) \stepstopol \pol_2}
           {\mpstate{\mach_1}{\pol_1} \stepstoobs{\obs}_P \mpstate{\mach_2}{\pol_2}}\]

@@

    We project the machine states from either machine trace with \(\pi_m\) and the observations with \(\pi_o\).
    An observational prefix \(\obsT_1 \lesssim \obsT_2\) means that the trace \(\obsT_1\) of observations is
    a prefix of \(\obsT_2\) up to the deletion of \(\tau\) observations:
    \leo{Point out this is coinductive}

@@

    \[\frac{\neg \isinf(\MPT) \hspace{.5cm} \mathit{Obs}(\MPT) \lesssim \mathit{Obs}(\machT)}
           {\MPT \sim_P \machT}\]

    \[\frac{\isinf(\MPT) \hspace{.5cm} \mathit{Obs}(\MPT) \simeq \mathit{Obs}(\machT)}
           {\MPT \sim_P \machT}\]

@@

    \paragraph*{Call Maps and Returns}

    A {\it call map} identifies machine states that represent a call, abstracting away the explicit
    calling convention. Formally it maps some machine states to a number of arguments:
    \[\callmap \in \CALLMAPS = \MACHS \rightharpoonup \mathbb{N}\]

@@

    \[\begin{split}
      \ret{\mach_c}\ \mach_r \triangleq & \mach_r(\PCname) = \next(\mach_c(\PCname)) \land \\
                                        & \mach_r(\SP) = \mach_c(\SP)
    \end{split}\]

    \leo{TODO: Initial state depends on call map}

    \paragraph*{Stack safety}

@@

      \leo{Think more about whether we vary mc or step mc}

@@

      Observable confidentiality is concerned with whether high confidentiality data influences
      observable both behavior during and after a call. We define variants given the generalized notion
      of contours:
      \[\mach \approx_\contour \mach' \triangleq \forall \component .
      \contour(\component) = \LOWSEC \rightarrow \mach(\component) = \mach'(\component)\]
      \leo{Move earlier}

      Data that is high confidentiality within a callee due either to being in its caller's frame
      will become low confidentiality if the callee returns.\leo{??} We face a subtle distinction: 
      a callee treats the contents of its caller's frame as secrets, and they should not influence
      its behavior. Nor should the callee be able to influence behavior after its return based
      on the caller's secrets, for instance by copying them to registers that will later be output.
      But the caller itself may still adjust its behavior based on its own secrets. So our property
      relies on another rollback function to preserve changes made by the caller but remove other
      differences between variant states.

      In this case, a confidentiality rollback takes a contour and four states: two call states
      that will be variants, and two return states. It is not symmetric, regarding \(\mach_c\) and \(\mach_r\)
      as the ``real'' call and return, \(\mach_c'\) as a variant and \(\mach_r'\) as a return that follows it.
      \[\begin{split}
        & \mathit{roll}_C(\contour,\mach_c,\mach_c',\mach_r,\mach_r')(\component) = \\
        & \begin{cases}
          \mach_c(\component) & \text{if } C(\component) = \HIGHSEC \text{ and } \\
                  & \mach_c(\component) = \mach_r(\component) \text{ and }
                    \mach_c'(\component) = \mach_r'(\component) \\
          \mach_r'(\component) & \text{else} \\
        \end{cases}
      \end{split}\]
      \leo{Maybe this should be called unscramble}

@@

      \leo{Need to fix append. Maybe call it join. It should remove the last
        state of left arg}
